% 
% This is Rick Battle's Masters Thesis
%

\documentclass[twoside,thesis,twoadvisors]{npsreport} 

% Title Page

\title{Thrashing and Locality in Modern Linux Systems}
\author{Rick Battle}
\rank{LTJG, USN}
\prevdegrees{B.S. Computer Engineering, Virginia Tech, 2009 }

\degree{Master of Science in Computer Science}
\degreeabbreviation{MS}
\department{Department of Computer Science}
\thesisadvisorone{Dr. Peter Denning}
\thesisadvisortwo{Dr. Craig Martell}
\departmentchair{Dr. Peter Denning}


\degreedate{September 2013} 
\distribution{Approved for public release; distribution is unlimited}
\abstract{This thesis is an exploration of the need for thrashing prevention techniques in the modern Linux Kernel in light of large scale systems. }

% Information for the SF298.
% These are mandatory:
\ReportType{Master's Thesis}
\DatesCovered{2102-06-01---2104-10-31}
\SponsoringAgency{Department of the Navy}
\ReportClassification{Unclassified}
\AbstractClassification{Unclassified}
\PageClassification{Unclassified}

% These are optional:
\ContractNumber{}
\GrantNumber{}
\ProgramElementNumber{}
\TaskNumber{}
\WorkUnitNumber{}
\POReportNumber{}
\Acronyms{}
\SMReportNumber{}
\SupplementaryNotes{The views expressed in this thesis are those of
  the author and do not reflect the official policy or position of the
Department of Defense or the U.S. Government.  IRB Protocol number XXX.}
\SubjectTerms{}
\ResponsiblePerson{}
\RPTelephone{}

%
% your thesis begins here
%

\begin{document}

\NPScover                       % Cover
\NPSsftne                       % SF298
\NPSthesistitle                 % Title page
\NPSabstractpage                % Abstract Page
\NPSfrontmatter                 % NPS front matter follows

% This changes the chaptermark and includes the various tables

\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\chaptername}\ \thechapter.\ #1}{}}
\NPStableOfContents
\NPSlistOfFigures
\NPSlistOfTables

% I put the acknowledgements here
\NPSacknowledgements{
  I want to thank everybody who helped me get to where I am today.
}

% NPS body follows

\NPSbody

\chapter{Introduction to Thrashing and Locality}

If you got this far, then the front mater works.

\chapter{The Evolution of Thrashing and Locality}
Prior Work

\chapter{Thrashing, Locality, and Implemnting Working Set}
Methodology

\section{Demonstration of Thrashing}
Induced thrashing

\section{Demonstration of Temporal Locality}
Graphed memory usage patterns to demonstrate temporal locality.

\section{Implemntation of a Locally Controlled Working Set Policy}
Kernel hacking!!!

\chapter{Performance Measurements of the Locally Controlled Working Set Policy}
Graphs!!!

\chapter{Conclusions and Recommendations}
It Works!

\chapter{Future Work}
Long term maintenance.

% This is the official end of the thesis

% Appendices follow

%\NPSappendix
%\chapter{[APPENDEX NAME]}
%[APPENDEX BODY]

\begin{thebibliography}{1}  %number of references

\bibitem{working-set}
P. J. Denning, "The working set model for program behavior", Communications of the ACM 11, 5 (May 1968), 323-333.
  
\end{thebibliography}

\NPSend

% This is the official distribution list.
% Free free to comment out or add your own
% The list is automatically properly numbered.

\chapter*{Initial Distribution List}
\singlespace
\begin{enumerate}
\item Defense Technical Information Center\\Ft. Belvoir, Virginia
\item Dudly Knox Library\\Naval Postgraduate School\\Monterey, California
\item Marine Corps Representative\\Naval Postgraduate School\\Monterey, California
\item Directory, Training and Education, MCCDC, Code C46\\Quantico, Virginia
\item Marine Corps Tactical System Support Activity (Attn: Operations
  Officer)\\Camp Pendleton, California
\textit{Officer students in the Operations Research Program are also required
to show:}

\item Director, Studies and Analysis Division, MCCDC, Code C45\\
Quantico, Virginia

\textit{Officer students in the Space Ops/Space Engineering Program or in the
Information Warfare/Information Systems and Operations are also
required to show:}

\item Head, Information Operations and Space Integration Branch,\\
PLI/PP\&O/HQMC, Washington, DC
\end{enumerate}
\end{document}
